---
title: "Homework 2"
author: Paola Sanchez-Medina
output: html_notebook
---

1. Total Cost:
```{r}
# INPUT
price = 30000
taxRate = 0.07875

# PROCESSING
total = price * (1+taxRate)

# OUTPUT
print (total)
```


2. Basic Accounting Formula:
```{r}
# INPUT
assets = 10000
liabilities= 5000

# PROCESSSING
equity = assets - liabilities

# OUTPUT
print (equity)
```


3. Net Income:
```{r}
# INPUT
revenue = 12000
expenses = 2000

# PROCESSING
netIncome = revenue - expenses

# OUTPUT
print (netIncome)
```


4. Break Even Point:
```{r}
# INPUT 
fixedCosts = 700
salesPricePerUnit = 10
variableCostsPerUnit = 3

# PROCESSING
breakEvenPoint = fixedCosts/ (salesPricePerUnit- variableCostsPerUnit)

# OUTPUT
print (breakEvenPoint)
```


5. Cash Ratio:
```{r}
# INPUT
cash = 2000
currentLiabilities = 6000

# PROCESSING
cashRatio = cash/currentLiabilities

# OUTPUT
print (cashRatio)
```


6. Current Ratio:
```{r}
# INPUT
currentAssets = 2000 + 4000
currentLiabilities = 6000

# PROCESSING
currentRatio = currentAssets/currentLiabilities

# OUTPUT
print (currentRatio)
```


7. Profit Margin Percentage:
```{r}
# INPUT
netIncome = 1000
sales = 2000

# PROCESSING
profitMarginPercentage = (netIncome/sales)* 100

# OUTPUT
print (profitMarginPercentage)
```


8. Markup Percentage:
```{r}
# INPUT
priceOfGood = 5
costOfGoodSold = 2

# PROCESSING
markupPercentage = ((priceOfGood- costOfGoodSold)/ costOfGoodSold) *100

# OUTPUT
print (markupPercentage)
```


9. Debt to Equity Ratio:
```{r}
# INPUT
totalLiabilities = 5000
totalEquity = 10000

# PROCESSING
debtToEquityRatio = totalLiabilities/ totalEquity

# OUTPUT
print (debtToEquityRatio)
```


10. Cost of Goods Sold:
```{r}
# INPUT
beginningInventory = 10000
costOfPurchasingNewInventory = 5000
endingInventory = 8000

# PROCESSING
COGS = beginningInventory + costOfPurchasingNewInventory - endingInventory

# OUTPUT
print (COGS)
```


11. Retained Earnings:
```{r}
# INPUT
beginningRetainedEarnings = 100000
netIncome = 50000
cashDividends = 25000

# PROCESSING
retainedEarnings = beginningRetainedEarnings + netIncome - cashDividends

# OUTPUT
print (retainedEarnings)
```


12. Return on Investment:
```{r}
# INPUT
investmentGain = 1500
investment = 1000
# PROCESSING
returnOnInvestment = (investmentGain- investment)/ investment

# OUTPUT
print (returnOnInvestment)
```


13. Inventory Shrinkage Percentage:
```{r}
# INPUT
recordedInventory = 500
actualInventory = 100

# PROCESSING
inventoryShrinkagePercentage = ((recordedInventory - actualInventory) / recordedInventory) *100

# OUTPUT
print (inventoryShrinkagePercentage)
```


14. Future Value:
```{r}
# INPUT
cash = 10000
rateOfReturn = 0.15
time = 35

# PROCESSING
futureValue = cash * (1+ rateOfReturn)^time

# OUTPUT
print (futureValue)
```


15. Present Value:
```{r}
# INPUT
futureValue = 10057
rateOfReturn = 0.15
time = 5

# PROCESSING
presentValue = futureValue / (1+rateOfReturn)^time

# OUTPUT
print (presentValue)
```


16. Simple Interest:
```{r}
# INPUT
principal = 20000
rate = 0.015/100
time = 30

# PROCESSING
simpleInterest = principal * rate * time

# OUTPUT
print (simpleInterest)
```


17. Compound Interest:
```{r}
# INPUT
principal = 10000
rate = 0.15
compoundings = 4
time = 35

# PROCESSING
amount = principal * (1+ (rate/compoundings))^ (compoundings * time)

# OUTPUT
print (amount)
```


18. Effective  Rate:
```{r}
# INPUT
rate = 0.15
compoundings = 4

# PROCESSING
effectiveRate = (1+(rate/compoundings))^compoundings - 1

# OUTPUT
print (effectiveRate)
```


19. Amortized Loan Payment:
```{r}
# INPUT
amountBorrowed = 250000
periodicInterestRate = 0.004167
numberOfPayments = 360

# PROCESSING
amortizedLoanPayment = (amountBorrowed* periodicInterestRate) / (1-(1+ periodicInterestRate)^-numberOfPayments)

# OUTPUT
print (amortizedLoanPayment)
```


20. Remaining Balance:
```{r}
# INPUT
regularPayment = 1342.115
periodicInterestRate = 0.004167
numberOfPayments = 360
numberOfPaymentsAlreadyMade = 241

# PROCESSING
remainingBalance = regularPayment * ((1-(1+ periodicInterestRate)^-(numberOfPayments- numberOfPaymentsAlreadyMade))/ periodicInterestRate)

# OUTPUT
print (remainingBalance)
```

